Predicting Counter-Strike Win Rates Using Player Statistics

### 2024-04-19 paper/paper.qmd
addressed flaw in data

>>>>

One minor flaw in the data is the total number of losses is one less than the number of wins when they should be equal. This could
be caused by an error in the data collection or an error by HLTV.org. It is not possible to determine the cause without rescraping all the data,
which takes a long time. This error likely makes very little difference in the results and can probably be ignored. Improvements can be made in the future to
the scraper so it detects these types of errors during runtime instead of after all the data has been collected.
